Robust and Efficient CSI Compression Using CLLWCsiNet in Noisy MIMO Environments

### 2025-03-30 paper_latex_edit - Copy.tex
txs auto checkin

where  \begin{math} \ F_{d}\in \textbf{C}^{N_{c}\times N_{c}}\end{math} is delay DFT and \begin{math} \ F_{a}\in \textbf{C}^{N_{t}\times N_{t}}\end{math} is angular DFT.

>>>>

where  \begin{math} \ F_{d}\in \textbf{C}^{N_{c}\times N_{c}}\end{math} is delay DFT and \begin{math} \ F_{a}\in \textbf{C}^{N_{t}\times N_{t}}\end{math} is angular DFT and both of them are unitary DFT matrices.
